Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-02-21 RET_Hosts.tex
Updates from Overleaf

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Supernova hosts in DES]{Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. Wiseman et al.]{
P. Wiseman$^1$\thanks{E-mail: p.s.wiseman@soton.ac.uk (PW)},
 M. Pursiainen$^1$,
 M. Smith$^1$,
 M. J. Childress$^1$,
 and Other Authors$^{1,2}$,
\newauthor
(The DES Collaboration)
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Southampton, Southampton, SO17 1BJ, UK\\
$^{2}$Other Institutions\\
%$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey. This number expands upon the 72 of \citetalias{Pursiainen2018}. and is presented in a companion work \citetalias{Pursiainen2020}.

@@

As for SFR, we show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}. The RET hosts are clearly shifted higher sSFRs than CCSNe. This result is significant as there are no obvious selection effects which could cause the shift.

\subsection{Metallicity \label{subsec:res_metallicity}}
\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_OH_cum.png}
\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:oh_cum}}
\end{figure}

\begin{figure*}
\includegraphics[width=\textwidth]{figs/RET_MZR.png}
\caption{The mass-metallicity relation (MZR) for RET host galaxies.
\label{fig:mzr}}
\end{figure*}

@@

In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars. A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity. Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we can compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies. The cumulative distributions of metallicity are displayed in \ref{fig:oh_cum}, and show RET hosts to be consistent with CCSNe and field galaxies. While the RET curve lies at lower metallicity than CCSNe and field galaxies in the $8.4 < \log \left(12+\textrm{O/H}\right)<9.0$ range, this is entirely within the $1\sigma$ uncertainty region for the RET host CDF. In Fig.~\ref{fig:mzr} we show the mass-metallicity relation (MZR) for the RET and comparison samples.

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Supernova hosts in DES]{Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients}
% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. Wiseman et al.]{
P. Wiseman$^1$\thanks{E-mail: p.s.wiseman@soton.ac.uk (PW)},
 M. Pursiainen$^1$,
 M. J. Childress$^1$,
 M. Smith$^1$,
 and Other Authors$^{1,2}$,
\newauthor
(The DES Collaboration)
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Southampton, Southampton, SO17 1BJ, UK\\
$^{2}$Other Institutions\\
%$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

@@

We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey. This number expands upon the 72 of \citetalias{Pursiainen2018}. The first reason for the increased sample size is the use of the 5th year of DES-SN, where \citetalias{Pursiainen2018} were only able to make use of the first four years. The second reason is an update to the sample selection technique. In \citetalias{Pursiainen2018}, objects were highlighted based on various lightcurve criteria such as time of rise to peak brightness ($t_{\mathrm{rise}}$), time of decline ($t_{\mathrm{decl}}$), and lightcurve `full-width half-maximum' ($t_{\mathrm{FWHM}}$). Candidates fitting these criteria were then vetted manually in order to make the final sample. The manual vetting included a removing a large number of active galactic nuclei (AGN). In this work, we expand upon this procedure with the introduction of a machine learning technique

@@

As for SFR, we show the cumulative distribution of sSFR in Fig.~\ref{fig:ssfr_cum}. The RET hosts are clearly shifted to higher sSFRs than CCSNe. To compare statistically the host sSFR distribution of RETs with the other samples, we employ the method of \citet{Wiseman2020}. For each pair of samples, we model the PDFs as skewed normal distributions. For both samples, we use identical normal priors for the `mean' and `scale'\footnote{See \citet{Wiseman2020} for a detailed description of the parameters describing the skewed normal distributions}, centred on the mean and twice the standard deviation of the two samples combined.

\subsection{Metallicity \label{subsec:res_metallicity}}
\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_MZR.png}
\caption{The mass-metallicity relation (MZR) for RET host galaxies.
\label{fig:mzr}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_OH_cum.png}
\caption{Cumulative distributions of the gas-phase oxygen abundances of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:oh_cum}}
\end{figure}

@@

In the Section \ref{subsec:res_sfr} we demonstrate that RETs occur in galaxies with systematically higher sSFR than CCSNe, to which one explanation is that they are related to more massive stars. A further property that could directly impact the composition of stellar populations harbouring potential RET progenitors is the metallicity. Using the gas-phase oxygen abundances calculated in Section \ref{subsec:calc_Z} as a proxy for metallicity, we can compare the chemical state of RET host galaxies with CCSNe and star-forming field galaxies. The cumulative distributions of metallicity are displayed in \ref{fig:oh_cum}, and show RET hosts to be inconsistent with SNe II and field galaxies. The RET curve lies at lower metallicity than those galaxies, and appears visually similar to the curves for SESNe. RETs occur, on average, in slightly more metal-rich environments than LGRBs and SLSNe.

We compare the metallicity distributions in the same way as the sSFRs. The RET host metallicity distribution is significantly different to the SNe II and SDSS distributions, with no overlap in the posterior distributions for the skewed-normal distribution peak and skewness. On the other hand, simultaneous fits with SESNe show very similar distributions.

In Fig.~\ref{fig:mzr} we show the mass-metallicity relation (MZR) for the RET and comparison samples.
